Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0 (copy).tex
IEEE Trans on Sustainable Energy paper

The authors would like to thank: (i) Newton Fund [grant $261881580$] for the mobility support; (ii) FAPEAM - Amazonas Foundation for Research [PROTI-Pesquisa $2018$], for the mobility support to UK (NOV-$2018$); (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and (iv) University of Sheffield's QR GCRF Institutional Allocation for the HOMER Pro license.

>>>>

The authors would like to thank to University of Sheffield's QR GCRF for HOMER license.

The authors would like to thank: (i) Newton Fund [grant $261881580$] for the mobility support; (ii) FAPEAM - Amazonas Foundation for Research [PROTI-Pesquisa $2018$], for the mobility support to UK (NOV-$2018$); (iii) FAS - Sustainable Amazonas Foundation for the PhD scholarship (NOV-$2017$ to MAR-$2019$); and
